\documentclass{article}
\usepackage{scimisc-cv}

\title{Nischals' Resume}
\author{Nischal Srinivas Basuti}
\date{June 2020}

%% These are custom commands defined in scimisc-cv.sty
\cvname{Nischal Srinivas Basuti}
\cvpersonalinfo{
+66 61-827-0147 \cvinfosep
nischalbasuti1@gmail.com \cvinfosep
github.com/nischalbasuti \cvinfosep
linkedin.com/in/nischalbasuti
}

\begin{document}

% \maketitle %% This is LaTeX's default title constructed from \title,\author,\date

\makecvtitle %% This is a custom command constructing the CV title from \cvname, \cvpersonalinfo

\section{Education}
\textbf{JNTUH, College of Engineering Hyderabad} -- Kukatpally, Hyderabad (2016-present)

\textbf{Asian Institute of Technology, School of Engineering} -- Bangkok, Thailand (2018-present)

Currently persuing B.Tech (Computer Science) and M.E.(Computer Science) dual degree. 

\cvsubsection{Under Graduate Major Project}[JNTUH]
[][August 2016 - December 2016]

\begin{itemize}
    \item An Android Muliticasting application developed in a team of three. I was responsible for designing the system architecture, front-end development and database schema.
    \item Tools Used: Android SDK, Firebase Cloud Platform, and Node.js
\end{itemize}
 
\cvsubsection{Software Architecture and Design Final Project}[AIT]
[][August 2016 - December 2016]
\begin{itemize}
    \item  Payment system through QR code for a coffee shop on campus leveraging the cafeterias credit system linked to
    student emails developed by the whole class (10 students).
    \item I was responsible for developing the customers' Android application, deploying of the back-end application and
    setting up the database.
    \item Tools used: Java EE (Glassfish), Hibernate, Android SDK.
\end{itemize}

\cvsubsection{Software Architecture and Design Final Project}[AIT]
[][August 2016 - December 2016]
\begin{itemize}
    \item Payment system through QR code for a coffee shop on campus leveraging the cafetrias credit system linked to student emails developed by the whole class (10 student).
    \item I was responsible for developing the customers' Android application, deploying of the back-ned application and setting up the database.
    \item Tools used: Java EE (Glassfish), Hibernate, Android SDK.
\end{itemize}

\cvsubsection{Machine Learning Final Project}[AIT]
[][August 2016 - December 2016]
\begin{itemize}
    \item Developed a recurrent neural network for stock market prediction in a team of 3.
    \item Tools used: Python, TensorFlow.
\end{itemize}

\cvsubsection{Machine Vision Final Project}[AIT]
[][August 2016 - December 2016]
\begin{itemize}
    \item Developed a Convolutinal Neural network to detect shadows.
    \item Tools used: Python, Keras, OpenCV.
\end{itemize}

\cvsubsection{Web Application and Engineering Final Project}[AIT]
[][August 2016 - December 2016]
\begin{itemize}
    \item A web application to organize events and activities for the student union. Features include user role management site-wide and per event, scheduling of events and activities within the event, and bulletins for participants to interact with the event organizers.
    \item  I was responsible for setting up and maintaining a server from scratch on a blank virtual machine on the University's server as well as implement the core functions of the application.
    \item Tools used: Apache, Passenger, Ruby on Rails, JavaScript, jQuery, PostgreSQL, Jenkins CI, git.
\end{itemize}
 
\section{Internships}
\cvsubsection{Nestor Analytics}[Hyderabad][Web Developer][January 2017 to April 2017]

\begin{itemize}
    \item I was part of the technical team of five engineers building an educational software for schools.
    \item Worked mainly in JavaScript (jQuery, D3.js) along with HTML and CSS.
    \item Coordinated with product designers and data analysts to develop, design and implement products.
    \item Developed in-house tools in Python for natural language processing and data conversion / cleansing.
    \item Performed technical screening of interviewees.
\end{itemize}

\cvsubsection{Nimble}[Bangkok][Software Developer][July 2019 to January 2020]

\begin{itemize}
    \item I was part of the engineering team working on a loyalty-reward platform for a large retail company.
    \item Maintain and migrate old API codebase written in PHP/Drupal to Ruby on Rails.
    \item Build new version of API in Ruby on Rails following agile methodologies and test driven development.
    \item Collaborate with mobile teams, front-end web teams and project managers to decide on API design and implementation and story point estimations.
    \item Perform code reviews.
\end{itemize}

\section{Activites}

\cvsubsection{Flipkart Android Hackathon}[Hyderabad][][March 2016]
\begin{itemize}
\item Qualified along with 30 other programmers from all over India through an online codesprint on Hackerranker.
\item Won first prize along with two team members.
\item Successfully coordinated with teammates to build a web-service as a back-end to our android application.
\end{itemize}

\section{Technical Skills}
\subsection{Languages, Frameworks and Libraries}
\begin{itemize}
\item Fluent in Ruby (Rails) and Python (Flask, Django, SQLAlchemy)
\item Experience with JavaScript (JQuery, React-native, node.js), C++ (OpenGL, OpenCV) and Python (Tensorflow, keras, OpenGL, OpenCV)
\item Competent with Java, PHP, C and shell scripting.
\item Working knowledge and Android SDK and React Native.
\end{itemize}

\subsection{Other tools and technologies}
\begin{itemize}
\item JIRA for project management and issue tracking.
\item Experienced with git.
\item Github and Bitbucket for collaborating.
\item Familiar with Docker and AWS web services.
\item Comfortable working on any POSIX compliant system.
\item Working knowledge of RDBMS’s such as MySQL, PostgreSQL and SQLite.
\end{itemize}

\end{document}
